### 2018-04-04 paper/algorithm.tex
Adds figures of incremental OR and prob route tree

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{figures/schema.pdf}
\caption{\label{fig:pipeline}Pipeline of the steps undergone by Alice when he shares a file from his laptop L with Bob.}
\end{figure}

>>>>

Alice has a file \(f\) stored on one of her devices and wants to transfer \(f\) 
to Bob.
Neither Alice nor Bob care about where \(f\) will be stored, as long as they can 
access it from any device (\ie the device they are using at the moment).
Here we will focus on how to get \(f\) from any of Alice's devices to any of 
Bob's devices.
When \(f\) is available on any of Bob's devices, Bob can rely on the Device 
Swarm Protocol (\cref{DeviceSwarmProtocol}) to access it on the device choice.

\begin{figure*}
  \centering
  % XXX Replace ProbabilisticRoutes figure
  \includegraphics{figures/probabilistic-routes-cropped.png}
  \caption{\label{ProbabilisticRoutes}%
    Probabilistic routes from Alice to Bob.
  }
\end{figure*}

\begin{figure*}
  \centering
  % XXX Replace IncrementalOnionRouting figure
  \includegraphics[height=\textheight]{figures/incremental-onion-routing-cropped.png}
  \caption{\label{IncrementalOnionRouting}%
    Overview of incremental onion routing.
  }
\end{figure*}
